%*******************************************************
% Prefazione 
%*******************************************************


\myChapter*{Aphorisms}
\markboth{\spacedlowsmallcaps{Aphorisms}}{\spacedlowsmallcaps{Aphorisms}} 
%\mtcaddchapter[\numberline{}\tocEntry{Aphorisms}]

		   \addtocontents{toc}{\protect\vspace{\beforebibskip}}
\addcontentsline{toc}{chapter}{\numberline{}\tocEntry{Aphorisms}}


The \emph{lietemotiv} of these notes is \emph{renormalization}. Let's sketch a
summary to grab the key
ideas. The section is mainly inspired by the introductory chapter of
Zinn-Justin.

QFT in its most direct formulations run into a severe conceptual
issue.
%with a \emph{severe conceptual
%   drawback}, namely the appearance of infinities in the
%calculation  of physical quantities. 
QFT crashes due to the occurrence of infinities in the calculations of physical
quantities.

%That's awful. QFT seems to have no predictive power. 
To overcome this difficulty and avoid the occurrence of infinities, an empirical, somewhat \emph{ad hoc} (but
systematic) procedure,
which goes under the name of renormalization, was eventually developed which allows extracting from
(meaningless) divergent mathematical expressions
(meaningfull) finite numerical predictions to be compared with experiments.


Often in mathematics one meets expressions which naively speaking are divergent
but it is possible to append a meaning to them, \eg, via analytic continuation or by
regularize them in a suitable way.
Renormalization however is a different story.
Experimental data are needed in order the renormalization algorithm to work.
Renormalization recipe needs input from experiments.
You have to provide \emph{input} experimental parameters in order the
renomalization machinary to work. 
The divergence is hidden behind some experimental parameters, it's not a purely
mathematical fact like analytic continuation.
Renormalization heals the divergences of the theory by sweep them 
under the carpet of few external parameters.
In other words, infinities are absorbed into few experimental parameters.

The renormalization recipe works in this spirit: you have to carefully
distinguish between \emph{bare} quantities (\eg, mass, electric charge) and
\emph{effective}
quantities. The latter ones are those which actually have to be related to
experiments, while the former ones are additional auxiliary parameters of the
physical model, which are necessary in order the renormalization recipe to work
but whose physical meaning remains somewhat obscured.
At this level, it might be said that renornalization is a way of organizing the
calculations in order to get finite results from expressions which naively
speaking would otherwise led to infinities.

From a pragmatic point of view, 
renormalization works: It 
has allowed and still allows calculations of increasing precision.
In fact, the renormalization procedure would hardly have been convincing if the
predictions were not confirmed with increasing precision by experiments.

However, this is not the whole story. 
A beautiful and deep idea comes at this point of the story, which goes at the
heart of renormalization. 
   The problem of infinities is related to an unexpected phenomenon:
   \emph{Renormalization is related to the non-decoupling of very different
      lenght scales}.
   This idea was borned in the context of statistical mechanics of critical
   phenomena first, and then
   extended to particle physics. 
Today, those who are familiar with Kenneth Wilson's ideas and the renormalization
group, will immediately say that actually there is no divergence.
More or less, the story goes like this: 
Every QFT requires an ultraviole completion (thus being an effective theory).
The only difference between renormalizable and non-renormalizable QFTs lies in
the fact that the former are \emph{insensitive} to the ultraviolet data (which
can be absorbed in a few low-energy parameters) while the latter depend on the
details of the ultraviolet completion.
In other words, the fact whether the renormalization recipe is capable of absorbing the
divergences or not for a given quantum field theory and how, 
tells us an important property of the quantum field theory. 



 
